The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
fig 1 comments = done

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} \&~\ref{E:pz2} with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Note to self: Give parameter values.}
\rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.  Use  thicker line width for the actual histogram.  Change legend to say  ``$p_1(z)$ (Eq. 1)'' and ``$p_2(z)$ (Eq. 2)'' rather than giving the actual equation.  Also, why are two of the horizontal lines in the bottom panel solid and one dashed?  What decides the style for eachline?  Finally, I think it makes sense to plot $\delta$ rather than $1+\delta$.}}
\arun{Done. But I refer to the equations in the caption instead of the legend.}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

The parametric redshift distributions that we use are
\begin{equation}\label{E:pz1}
 p_1(z) \propto z^{a-1}\exp({-bz})
\end{equation}
and 
\begin{equation}\label{E:pz2}
 p_2(z) \propto z^2\exp{\left(-\left(\frac{z}{z_0}\right)^{1.5}\right)},
\end{equation}
the latter of which was first presented by
\cite{Redshift_modelling}. Here $a$, $b$, and
$z_0$ are free parameters that are to be determined.  The
normalization constants depend not only on the parameters but also on
the lower and the upper limit of the redshifts considered, where we
fix the normalization to ensure that the predicted number of galaxies
in the range used ($0.3<z<1$) is equal to the actual number. 
Fig.~\ref{fig:redshift_fluxlimited} shows the photometric redshift
histogram together with the best-fitting parametric distributions.
\rachel{The results for the 2nd redshift distribution do not look that
  great.  Does it help if we go to $z<1.25$?  I thought the photo-$z$
  were okay in that regime, and it's only beyond $1.25$ that they get
  really scary.  We could use up to $1.25$ for determining the
  redshift distribution, even if we're only trying to find
  overdensities for $z<1$.}

>>>>

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} \&~\ref{E:pz2} with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Note to self: Give parameter values.}
}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

The parametric redshift distributions that we use are
\begin{equation}\label{E:pz1}
 p_1(z) \propto z^{a-1}\exp\left[{-bz}\right]
\end{equation}
and 
\begin{equation}\label{E:pz2}
 p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
\end{equation}
the latter of which was first presented by
\cite{Redshift_modelling}. Here $a$, $b$, and
$z_0$ are free parameters that are to be determined.  The
normalization constants depend not only on the parameters but also on
the lower and the upper limit of the redshifts considered, where we
fix the normalization to ensure that the predicted number of galaxies
in the range used ($0.3<z<1$) is equal to the actual number. 
Fig.~\ref{fig:redshift_fluxlimited} shows the photometric redshift
histogram together with the best-fitting parametric distributions.
\rachel{The results for the 2nd redshift distribution do not look that
  great.  Does it help if we go to $z<1.25$?  I thought the photo-$z$
  were okay in that regime, and it's only beyond $1.25$ that they get
  really scary.  We could use up to $1.25$ for determining the
  redshift distribution, even if we're only trying to find
  overdensities for $z<1$.}
